### 2020-04-13 draft_ABP.tex
Updates from Overleaf

From the following equations for facets $\{F_{ij}\}$ of $A_n$
\[
F_{ac}+F_{bd}-F_{bc}-F_{ad}=\sum_{a\leq p<b\atop{c\leq q<d}}c_{pq}
\]
for $1\leq a<b<c<d\leq n+3$, ({\bf Zhenjie}: I conjecture that) we find the most economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
\begin{align*}
    &F_{ac}+F_{bd}-F_{ad}=\sum_{a\leq p<b< q<d}c_{pq}\quad \text{for $a<b<c=b+1<d$ }\\
    \text{or}&\\
    &F_{1c}+F_{b,n+3}-F_{bc}=\sum_{1\leq p<b\atop{c\leq q<n+3}}c_{pq}\quad \text{for $a=1$ and $d=n+3$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $c$s in several above equations. 
%We should see what happens when we set $c$s to be zero in only one above equations: 
{\bf (proof?)}

The basic idea for counting: Suppose that
\[
F_{ac}+F_{bd}-F_{ad}=0.
\]
Since $F_{ad}$, $F_{bd}$, $F_{ac}\geq 0$, the above equation force $F_{ac}$ and $F_{bd}$ to be zero when $F_{ad}=0$. Therefore, $F_{ad}$ cannot be a true facet of the degeneration. We should count the number of deleted $c$ and such spurious facets. They should be equal.

>>>>

From the following equations for facets $\{F_{ij}\}$ of $A_n$
\[
F_{ac}+F_{bd}-F_{bc}-F_{ad}=\sum_{a\leq p<b\atop{c\leq q<d}}c_{pq}
\]
for $1\leq a<b<c<d\leq n+3$, ({\bf Zhenjie}: I conjecture that) we find the most economical way to get a degeneration which satisfies the above property is setting all $c$s on the RHS of 
\begin{align*}
    &F_{ac}+F_{bd}-F_{ad}=\sum_{a\leq p<b< q<d}c_{pq}\quad \text{for $a<b<c=b+1<d$ }\\
    \text{or}&\\
    &F_{1c}+F_{b,n+3}-F_{bc}=\sum_{1\leq p<b\atop{c\leq q<n+3}}c_{pq}\quad \text{for $a=1$ and $d=n+3$}
\end{align*}
to be zero, and all wanted degenerations can be got by setting $c$s in several above equations.

We can see what happens from mesh when we set $c$s to be zero in only one above equations: an equation above corresponds a big diamond whose top or bottom corner and all $c$s are zero. For example,
\begin{center}
	\begin{tikzpicture}
		\draw (-2,0) node[left] {$A$} -- (1,-3) node[below] {$0$}
		-- (3,-1) node[right] {$C$} -- (0,2) node[above] {$B$}-- cycle;
		\draw (-1,-1) -- (1,1);
		\draw (-1,1) -- (2,-2);
		\draw (0,-2) -- (2,0);
			\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,2) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (-1,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (0,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,-1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,0) {};
	\end{tikzpicture}
\end{center}
this diamond tells us that
\[
A+C-B=0.
\]
Since $A,B,C\geq 0$, the above equation force $A$ and $C$ to vanish when $B=0$. Therefore, $B$ is no longer a facet of the degeneration. Similarly, it's pleasure to show that black points are all vanishing facets in the above example, and generally
the number of vanishing facets equals the number of deleted $c$s for degenerations of this type.

One can use these diamonds to build a degeneration with more vanishing facets. For example, in $A_3$
\begin{center}
\begin{tikzpicture}
	\fill[green!30] (2,1) -- (0,-1) -- (1,-2) -- (3,0);
	\fill[blue!30] (3,0) -- (2,-1) -- (3,-2) -- (4,-1);
	\draw[thick] (-2,-1) -- (1,2) -- (4,-1) -- (3,-2) -- (0,1);
	\draw[thick] (-1,-2) -- (2,1);
	\draw[thick] (-2,-1) -- (-1,-2);
	\draw[thick] (-1,0) -- (1,-2) -- (3,0);
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (1,0) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (2,1) {};
	\node[circle,draw=black, fill=black, inner sep=0pt,minimum size=5pt] at (3,0) {};
\end{tikzpicture}
\end{center}
after setting $c$s in green and purple diamonds to be zero, three facets (black points) vanish and building set after deletion is 
\[
\{\{0,1,2,3\},\{0,1,2\},\{0,1\},\{0\},\{1\},\{2\},\{3\}\}.
\]
One can further check that it's a cube or $A_1^3$.
